\section{Groups}

\subsection{Reminders from groups theory}

\begin{definition}[Group]
  \index{group}
  A group $G$ is a pair $(E, \cdot)$ where $E$ is a set and $\cdot$ is an operator: $\cdot: E \times E \to E$. A group must satisfies the following properties :
  \begin{itemize}
    \item \textbf{Associativity} $(a \cdot b) \cdot c = a \cdot (b \cdot c)\ \forall a,b,c \in G$.
    \item \textbf{Identity element} There exists an element of $G$ (we will call it $1$) such that $a \cdot 1 = a = 1 \cdot a \ \forall a \in G$.
    \item \textbf{Inverse element} $\forall a \in G$ there exists $a^{-1} \in G$ such that $a \cdot a^{-1} = 1 = a^{-1} \cdot a$.
  \end{itemize}
\end{definition}

\subsection{Permutation groups}

\paragraph{}
We will begin with some notions of permutation group. Those notions come from~\cite{cameronPermutationGroups}

\begin{definition}[Permutation]
  \index{permutation}
  A permutation of $S$ is a bijection between $S$ and itself. We can see it as a reordering of the elements of $S$.
\end{definition}

\paragraph{}
We will write permutation on the right, for example the application of the permutation $g$ to a point $\alpha$ is noted $\alpha g$ and not $g(\alpha)$. Permutations are composed left to right, so we write $\alpha gh$ instead of $h(g(\alpha))$. This can be confusing at the beginning be with this notation, we read from the left to the right and avoid changing reading (and reasonning) direction between each expression.

\paragraph{}
One popular way to write permutation is the following notation.

\[
  g =
  \left(
    \begin{array}{ccccc}
      1 & 2 & 3 & 4 & 5\\
      2 & 5 & 3 & 4 & 1
    \end{array}
  \right)
\]

\begin{definition}[Fixed point]
  \index{fixed point (permutation)}
  A fixed point of a permutation $g$ is a point $\alpha$ such that $\alpha g = \alpha$.
\end{definition}

\begin{definition}[Transposition]
  \index{transposition}
  A transposition is a permutation that swap two points and let all others points fixed.
\end{definition}

\paragraph{}
A transposition of the point $\alpha$ and $\beta$ is written $(\alpha\ \beta)$.

\begin{definition}[Cycle]
  \index{cycle (permutation)}
  \index{cyclic permutation}
  A \textit{cycle} or \textit{cyclic permutation} is a permutation which maps elements in a cyclic fashion. All other points are fixed.
\end{definition}

\paragraph{}
We note a cycle $(c_1\ c_2\ \dots\ c_n)$ where the $c_i$ are the elements moved by the cyclic permutation.

\paragraph{}
The term \textit{cyclic permutation} is used to describe a full permutation and the term \textit{cycle} is used to describe a part of a permutation. But the meaning remains the same.

\begin{proposition}
  Every cycle can be written as a product of transposition.
\end{proposition}

\begin{proof}
  \[
    (c_1\ c_2\ c_3\ \dots\ c_n) = (c_1\ c_2)(c_1\ c_3)\dots(c_1\ c_n)
  \]
\end{proof}

\begin{proposition}
  Every permutation can be written as a product of a cycles.
\end{proposition}

\begin{proof}
  For every non fixed-point $\alpha_0$, we can find a sequence defined by $\alpha_{i+1} = \alpha_i g$. There must be a $j \neq 0$ such that $\alpha_j = \alpha_0$. $g$ is a bijection between the same set. And so it's a bijection between two finite sets of the same size. But if the sequence does not loop back to its first element, it can't loop at all because it's a bijection. So it must be infinite and it's a contradiction
  % TOO COMPLICATED
\end{proof}

\begin{corollary}
  Every permutation can be written as a product of transposition.
\end{corollary}

\begin{definition}[Symmetric group]
  \index{symmetric group}
  Let $\Omega$ be a set, the group of all permutations of $\Omega$ is a called the symmetric group of $\Omega$ and is denoted $\Sym(\Omega)$. Most of the time, we do not care about the elements of $\Omega$, the only important thing about $\Omega$ is its size because the structure of $\Sym(\Omega)$ is only determined by this parameter. Therefore, we will mostly denote $S_n$ the symmetric group over an set of $n$ elements
\end{definition}

\begin{definition}[Permutation group]
  \index{permutation}
  A permutation group on a set $\Omega$ (resp. a set of $n$ points) is a subset of $\Sym(\Omega)$ (resp. $S_n$).
\end{definition}



\subsection{String group generated by involutions}

\begin{definition}[Involution]
  An element $g$ of a group is called an \textit{involution} if $g^2 = \id$.
\end{definition}

\begin{definition}[Indexed generated group]
  Let $G$ be a group and let $S = \{\rho_0, \dots, \rho_{r-1}\}$ be an indexed set of generators.
  We call the pair $(G,S)$ a \textit{indexed generated group}. Most of the time, we will denote it $\Gamma$.
\end{definition}

\begin{definition}[Rank of an indexed generated group]
  The rank of an indexed generated group is the number of generators, i.e. the size of $S$.
\end{definition}

\begin{definition}[Group generated by involutions]
  Let $\Gamma$ be an indexed generated group. If all the generators of this group are involutions, then this group is called a \textit{group generated by involutions}.
\end{definition}

\begin{definition}[String property]
  Let $\Gamma$ be an indexed generated group of rank $r$. If forall $0 \le i < r-1$, $\rho_i$ and $\rho_{i+1}$ commutes ($\rho_i \rho_{i+1} = \rho_{i+1}\rho_i$), then this indexed generated group has the \textit{string property}.
\end{definition}

\begin{definition}[String group generated by involution]
  If a group generated by involutions has the string property, we call it a \textit{string group generated by involution} or \textit{sggi}.
\end{definition}

\subsection{String C-groups}

\paragraph{}
Let $\Gamma = (G,S)$ be an indexed generated group. We will denote $\Gamma_I$ with $I \subseteq S$ the permutation group by $I$.

\begin{definition}[Intersection property]
  Let $\Gamma = (G,S)$ be a indexed generated group. If for all $I, J \subseteq S$, we have that $\Gamma_I \cap \Gamma_J = \Gamma_{I \cap J}$, we say that $\Gamma$ satisties the intersection property.
\end{definition}

\begin{definition}[String C-group]
  If a sggi satisfies the intersection property, we will say that is a $\textit{string C-group}$.
\end{definition}

\subsection{Properties of groups}

\begin{property}
  Let $\Gamma = \langle \rho_0, \dots, \rho_{r-1} \rangle$ be a sggi such that $\Gamma_0, \Gamma_{r-1}$ are string C-groups and $\Gamma_0 \cap \Gamma_{r-1} = \Gamma_{0,r-1}$ then $\Gamma$ is a string C-group.
\end{property}

\begin{property}
  Let $\Gamma$ be a sggi, if $\Gamma_0$ and $\Gamma_{r-1}$ are string C-group, $\rho_{r-1} \notin \Gamma_{r-1}$ and $\Gamma_0$ is maximal
\end{property}
