\subsection{Equality relations}

The definitions come from~\cite{polytopes} and~\cite{incidenceGeometry}

\begin{definition}[Equality relation]
  \index{equality relation}
  An equality relation $\sim$ on a set $E$ is a subset $R$ of $E \times E$. We write $x \sim y$ iff $(x,y) \in R$ with the following properties:
  \begin{enumerate}
    \item \textbf{Reflexivity} $x \sim x \ \forall x \in E$
    \item \textbf{Symmetry} $x \sim y \Leftrightarrow y\sim x \ \forall x,y \in E$.
    \item \textbf{Transitivity} if $x \sim y$ and $y \sim z$ then $x \sim z$ for all $x,y,z \in E$.
  \end{enumerate}
\end{definition}

\subsection{Posets}

\begin{definition}[Partially ordered set]
  \index{partially ordered set}
  \index{poset}
  A \textit{partially ordered set} or \textit{poset} is a pair $(P,\le)$ with $P$ a set and $\le$ a relation between $P$ and $P$ such that
  \begin{enumerate}
    \item \textbf{Reflexivity} $x \le x$ ($\forall x \in P$)
    \item \textbf{Anti-symmetry} if $x \le y$ and $y \le x$, then $x = y$ ($\forall x,y \in P$)
    \item \textbf{Transitivity} if $x \le y$ and $y \le z$, then $x \le z$ ($\forall x,y,z \in P$)
  \end{enumerate}
\end{definition}

\begin{definition}[Comparability]
  \index{comparability}
  Two elements $x$, $y$ of a poset are said to be \textit{comparable} if $x \le y$ or $y \le x$.
\end{definition}

\paragraph{}
This is called a \textit{partial} order because there is no constraint that implies that every pair of elements of $P$ is comparable, i.e. for $x,y \in P$ it is possible that neither $x \le y$ nor $y \le x$.

\paragraph{}
We denote $x < y$ when $x \le y$ and $x \neq y$.

\paragraph{}
\index{Hasse diagram}
Given a poset, we can draw its \textit{Hasse diagram}. It's a graph where the vertices are the elements of $P$ and two elements $x$ and $y$ are connected with $x$ under $y$ if $x \le y$. Therefore, no horizontal edge can exist.

\paragraph{}
We try to minimize the number of edges so we will not connect $x$ and $z$ (with $x \le z$) if there exists $y$ such that $x < y < z$. This is required otherwise the diagram becomes overloaded quickly. The reader can deduce the removed edge by transitivity.

\begin{figure}[H]
  \begin{center}
    \begin{tikzpicture}

      \begin{scope}[every node/.style={circle,draw}]
        \node (f)  at (2,6)  {f};
        \node (e)  at (0,6)  {e};
        \node (d)  at (0,4)  {d};
        \node (c)  at (2,2)  {c};
        \node (b)  at (0,2)  {b};
        \node (a)  at (1,0)  {a};
      \end{scope}

      \begin{scope}[every node/.style={fill=white,circle}]

        \begin{scope}[every edge/.style={draw}]
          \path (a)  edge (b);
          \path (a)  edge (c);
          \path (b)  edge (d);
          \path (d)  edge (e);
          \path (d)  edge (f);
          \path (c)  edge (f);
        \end{scope}
      \end{scope}

    \end{tikzpicture}
    \caption{Simple Hasse diagram}
  \end{center}
\end{figure}

\paragraph{}
In the figure, there is a link between $a$ and $b$ so $a \le b$, and $b \le d$. So $a \le d$ by transitivity, even if there is no line between those points.

\begin{definition}[Section]
  \index{section}
  Let $P$ be a poset and $x, z \in P$. The \textit{section} $[x,z]$ is the set of all elements $y \in P$ such that $x \le y \le z$.
\end{definition}

\begin{definition}[Connected poset]
  \index{connected poset}
  A poset $P$ is \textit{connected} if for every pair of elements $x, y$ there exists a sequence $x = x_0, x_1, \dots, x_{n-1}, x_n = y$ such that $x_i$ and $x_{i+1}$ are comparable for all $i$.
\end{definition}

\begin{definition}[Strongly connected poset]
  \index{strongly connected poset}
  A poset is said to be \textit{strongly connected} if every section of this poset is connected.
\end{definition}


\begin{definition}[Totally ordered set]
  \index{totally ordered set}
  A \textit{totally ordered set} is a poset in which every pair of elements is comparable.
\end{definition}

\begin{definition}[Chain]
  \index{chain}
  A \textit{chain} is a totally ordered subset of a poset.
\end{definition}

\begin{definition}[Maximal chain]
  A chain is called \textit{maximal} if it is not contained in any other chain.
\end{definition}

\begin{definition}[Ranked poset]
  \index{ranked poset}
  A poset is \textit{ranked} if there exists a function: $\rank : P \to \mathbb Z$ such that
  \begin{enumerate}
    \item if $x < y$, then $\rank(x) < \rank(y)$ $(x, y \in P)$
    \item if $x < y$ and if there exists no $z \in P$ such that $x < z < y$, then $\rank(y) = \rank(x) + 1$ $(x, y \in R)$.
  \end{enumerate}
\end{definition}

\paragraph{}
On the Hasse diagram, it means that, if all elements with the same rank are placed at the same level, an element in only connected to elements placed the level just above or just under itself.


\begin{figure}[H]
  \begin{center}
    \begin{tikzpicture}

      \node at (-4,6) {$r = 3$};
      \node at (-4,4) {$r = 2$};
      \node at (-4,2) {$r = 1$};
      \node at (-4,0) {$r = 0$};

      \draw[very thin, dashed] (-3,6) -- (5,6);
      \draw[very thin, dashed] (-3,4) -- (5,4);
      \draw[very thin, dashed] (-3,2) -- (5,2);
      \draw[very thin, dashed] (-3,0) -- (5,0);

      \begin{scope}[every node/.style={circle,draw,fill=white}]
        \node (f)  at (1,6)  {f};
        \node (e)  at (2,4)  {e};
        \node (d)  at (0,4)  {d};
        \node (c)  at (2,2)  {c};
        \node (b)  at (0,2)  {b};
        \node (a)  at (1,0)  {a};
      \end{scope}

      \begin{scope}[every node/.style={fill=white,circle}]

        \begin{scope}[every edge/.style={draw}]
          \path (a) edge (b);
          \path (a) edge (c);
          \path (b) edge (d);
          \path (b) edge (e);
          \path (c) edge (d);
          \path (c) edge (e);
          \path (d) edge (f);
          \path (e) edge (f);

        \end{scope}
      \end{scope}

    \end{tikzpicture}
    \caption{Poset with rank indication}
  \end{center}
\end{figure}

\begin{definition}[Diamond property]
  \index{diamond property}
  Let $P$ be a ranked poset. This poset satisfies the \textit{diamond property} iff given two elements $x$ and $y$ of $P$ such that $\rank(x) = \rank(y) - 2$ there exist exactly two elements $z_1$ and $z_2$ such that $x < z_1 < y$ and $x < z_2 < y$.
\end{definition}

  \subsection{Lattice}

  \begin{definition}[Upper bound, Lower bound]
    \index{upper bound}
    \index{lower bound}
    An upper (resp. lower) bound of two elements $x$ and $y$ is an element $m$ such that $x \le m$ and $y \le m$ (resp. $m \le x$ and $m \le y$).
  \end{definition}

  \begin{definition}[Supremum, Infinimum]
    \index{supremum}
    \index{infinimum}
    The supremum (resp. infinimum) of two elements $x$ and $y$ is the lower (resp. upper) bound in the set of all upper (resp. lower) bounds of $x$ and $y$. If it exists, it's unique. We denote the supremum of $x$ and $y$ $x \wedge y$, and the infinimum $ x \vee y$\footnote{À améliorer}.
  \end{definition}

  \begin{definition}[Lattice]
    \index{lattice}
    A lattice is a poset such that every pair of elements has a supremum and an infinimum.
  \end{definition}

  \paragraph{}
  It's not always clear whether a poset is a lattice or not, see for example the following diagram.

  \begin{figure}[H]
    \begin{center}
      \begin{tikzpicture}

        \begin{scope}[every node/.style={circle,draw}]
          \node (f)  at (1,6)  {f};
          \node (e)  at (2,4)  {e};
          \node (d)  at (0,4)  {d};
          \node (c)  at (2,2)  {c};
          \node (b)  at (0,2)  {b};
          \node (a)  at (1,0)  {a};
        \end{scope}

        \begin{scope}[every node/.style={fill=white,circle}]

          \begin{scope}[every edge/.style={draw}]
            \path (a)  edge (b);
            \path (a)  edge (c);
            \path (b)  edge (d);
            \path (b)  edge (e);
            \path (c)  edge (d);
            \path (c)  edge (e);
            \path (d)  edge (f);
            \path (e)  edge (f);

          \end{scope}
        \end{scope}

      \end{tikzpicture}
      \caption{Not a lattice: the infinimum of $d$ and $e$ is not unique}
    \end{center}
  \end{figure}
