\section{Groups}

\subsection{Groups and subgroups}

\begin{definition}[Group]
  \index{group}
  A group $G$ is a pair $(E, \cdot)$ where $E$ is a set and $\cdot$ is an operator $\cdot: E \times E \to E$. A group must satisfy the following properties:
  \begin{itemize}
    \item \textbf{Associativity} $(a \cdot b) \cdot c = a \cdot (b \cdot c)\ \forall a,b,c \in G$.
    \item \textbf{Identity element} There exists an element of $G$ (called $1$) such that $a \cdot 1 = a = 1 \cdot a \ \forall a \in G$.
    \item \textbf{Inverse element} $\forall a \in G$ there exists $a^{-1} \in G$ such that $a \cdot a^{-1} = 1 = a^{-1} \cdot a$.
  \end{itemize}
\end{definition}

\paragraph{}
Most of the times the symbol $\cdot$ is omitted and $g \cdot h$ is written $gh$.

\begin{definition}[Order]
  \index{order}
  The \textit{order} of a group is the number of elements in this group. It is denoted $|G|$.
\end{definition}

\begin{definition}[Abelian group]
  \index{abelian group}
  A group is said \textit{abelian} if for all $g, h \in G$
  \[
    g \cdot h = h \cdot g.
  \]
\end{definition}

\begin{definition}[Generating set of a group]
  \index{generating set}
  \index{generator}
  It is said that a set generates a group if all elements of the group can be written as a product of elements of this set. The elements of this set are called \textit{generators}. Conversely, no element outside the group can be written as a product of the generators.
\end{definition}

\begin{definition}[Subgroup]
  \index{subgroup}
  Let $G = (E, \cdot)$ be a group. A pair $H = (F, \cdot)$ of $G$ is a \textit{subgroup} of $G$ if $F \subseteq E$ and $H$ is a group.
\end{definition}

\begin{definition}[Proper subgroup]
  \index{proper subgroup}
  A subgroup $H$ is a proper subgroup of $G$ if $H \neq G$ and $H \neq {1}$.
\end{definition}

\begin{definition}[Coset]
  \index{coset}
  A \textit{coset} of a subgroup $H$ of $G$ is the product $gH = \{g \cdot h | g \in G, h \in H\}$ between an element $g \in G$ and $H$. If the group is not commutative, there are left and right cosets.
\end{definition}

\begin{property}
  If $G$ is a group and $H$ is a subgroup of $G$, every element $g \in G$ belongs to exactly one coset of $H$.
\end{property}

\begin{corollary}
  \label{magic-formula}
  The order of a subgroup divides the order of the group.
\end{corollary}

\begin{definition}[Normal subgroup]
  \index{normal subgroup}
  If the left cosets of a subgroup are the same as the right cosets, then this subgroup is called \textit{normal}.
\end{definition}

\begin{definition}[Simple group]
  \index{simple group}
  A group is \textit{simple} if it does not have any propert normal subgroup.
\end{definition}

\begin{definition}[Action]
  \index{action}
  Let $G$ be a group and $X$ a set, we say that $G$ acts on $X$ if there is an application
  \[
    \cdot : G \times X \Leftrightarrow X \qquad (x,g) \mapsto x \cdot g
  \]
  such that
  \begin{itemize}
    \item \textbf{Associativity} $(g \cdot h) \cdot x = g \cdot (h \cdot x)$
    \item \textbf{Identity} $ 1 \cdot x = x$ for all $x \in X$.
  \end{itemize}
\end{definition}

\begin{definition}[Degree]
  \index{degree}
  If a group $G$ acts on a group $X$, we say by abuse of language that the degree of $G$ is the size of $X$.
\end{definition}

\paragraph{}
Be careful because the symbol $\cdot$ can refer to different things depending on the operands.

\begin{definition}[Orbit of a element]
  \index{orbit}
  Let $X$ be a set and $G$ a group acting on it.
  The orbit of an element $x$ by the group $G$ is the subset
  \[
    O_x = \{g \cdot x | g \in G\}.
  \]
\end{definition}

\begin{definition}
  The stabilizer of an element $x\in X$ by a group $G$ is the set of elements of $G$ that lets $x$ fixed, i.e.
  \[
    G_x = \{g \in G | g \cdot x = x\}
  \]
\end{definition}

\begin{property}
  \label{orbit-stabilizer}
  If a group $G$ acts on a finite set $X$, then for every $x \in X$.
  \[
    |G| = |O_x||G_x|
  \]
\end{property}

\begin{definition}[Direct product]
  \index{direct product}
  Given two groups $G = (E, \star)$ and $H = (F, \Delta)$, the direct product $G \times H$ is a group $(E \times F, \cdot)$ such that
  \[
    (g_1, h_1) \times (g_2, h_2) = (g_1 \star g_2, h_1 \Delta h_2).
  \]
\end{definition}

\begin{definition}[Semidirect product]
  \index{semidirect product}
  \index{direct product}
  Given two groups $G = (E, \star)$ and $H = (F, \Delta)$, the semidirect product $G : H$ is a group $(E \times F, \cdot)$ such that
  \[
    (g_1, h_1) \times (g_2, h_2) = (g_1 \star \varphi(h_1,g_2), h_1 \Delta h_2)
  \]
  for a given $\varphi$.

  \paragraph{}
  In this case the product of the first component only depends on $h_1$ and not on $h_2$.
\end{definition}

\begin{definition}[Automorphism group]
  The automorphism group $\Aut(G)$ of a finite group $G$ is the set whose elements are the automorphisms $G \to G$ and where the group operation is the composition of automorphisms.
\end{definition}

\begin{definition}[Almost simple group]
  \index{almost simple group}
  A group $G$ is almost simple if there is a simple non-abelian group $S$ such that $S \le T \le \Aut(S)$ for $T$ isomorphic to $G$.
\end{definition}

\subsection{Permutation groups}

\paragraph{}
The followings statements about permutation groups come from~\cite{cameronPermutationGroups}.

\paragraph{}
In the context of permutations, the elements of set on which the group acts are called \textit{points}.

\begin{definition}[Permutation]
  \index{permutation}
  A permutation of a set $S$ is a bijection between $S$ and itself. It can be seen as a reordering of the elements of $S$.
\end{definition}

\paragraph{}
Instead of using the functional notation, the permutation will be written on the right on the composing read from the left to right. The application of the permutation $g$ to a point $\alpha$ is noted $\alpha g$ and not $g(\alpha)$. This make the notation lighter and the reading easier. So $\alpha gh$ will be written instead of $h(g(\alpha))$.

\paragraph{}
One common way to write permutation is the following notation:

\[
  g =
  \left(
    \begin{array}{ccccc}
      1 & 2 & 3 & 4 & 5\\
      2 & 5 & 3 & 4 & 1
    \end{array}
  \right)
\]

\paragraph{}
Here $1g = 2$ and $5g = 1$.

\begin{definition}[Degree of a permutation group]
  \index{degree}
  The \textit{degree} of a permutation group is the size of $S$.
\end{definition}

\begin{definition}[Fixed point]
  \index{fixed point (permutation)}
  A fixed point of a permutation $g$ is a point $\alpha$ such that $\alpha g = \alpha$.
\end{definition}

\begin{definition}[Transposition]
  \index{transposition}
  A transposition is a permutation that swaps two points and lets all others points fixed.
\end{definition}

\paragraph{}
A transposition of the points $\alpha$ and $\beta$ is written $(\alpha\ \beta)$.

\begin{definition}[Cycle]
  \index{cycle (permutation)}
  \index{cyclic permutation}
  A \textit{cycle} or \textit{cyclic permutation} is a permutation which maps elements in a cyclic fashion. All other points are fixed.
\end{definition}

\paragraph{}
We note a cycle $(c_1\ c_2\ \dots\ c_n)$ where the $c_i$'s are the elements moved by the cyclic permutation.

\paragraph{}
The term \textit{cyclic permutation} is used to describe a full permutation and the term \textit{cycle} is used to describe a part of a permutation. But the meaning remains the same.

\begin{proposition}
  Every cycle can be written as a product of transpositions.
\end{proposition}

\begin{proof}
  \[
    (c_1\ c_2\ c_3\ \dots\ c_n) = (c_1\ c_2)(c_1\ c_3)\dots(c_1\ c_n)
  \]
\end{proof}

\begin{proposition}
  Every permutation can be written as a product of cycles.
\end{proposition}

\begin{proof}
  For every non fixed-point $\alpha_0$, we can find a sequence defined by $\alpha_{i+1} = \alpha_i g$. There must be a $j \neq 0$ such that $\alpha_j = \alpha_0$. $g$ is a bijection between the same set. And so it's a bijection between two finite sets of the same size. But if the sequence does not loop back to its first element, it can't loop at all because it's a bijection. So it must be infinite and it's a contradiction.
\end{proof}

\paragraph{}
A new notation for permutations can now be introduced. Permutations will now be written as a product of cycles. This new notation does not include the total number of points. This must be clear in the context.

\begin{definition}[Symmetric group]
  \index{symmetric group}
  Let $\Omega$ be a set, the group of all permutations of $\Omega$ is called the symmetric group of $\Omega$ and is denoted $\Sym(\Omega)$. This is a group acting on $\Omega$. Often we do not care about the elements of $\Omega$, the only important thing about $\Omega$ is its size because the structure of $\Sym(\Omega)$ is only determined by this parameter. Therefore, we mostly denote $S_n$ the symmetric group over an set of $n$ elements.
\end{definition}

\begin{definition}[Permutation group]
  \index{permutation}
  A permutation group on a set $\Omega$ (resp. a set of $n$ points) is a subgroup of $\Sym(\Omega)$ (resp. $S_n$).
\end{definition}

\subsection{Transitive groups}

\begin{definition}[$k$-transitive group]\index{k-transitive group}
  A permutation group $G$ on $\Omega$ is called \textit{$k$-transitive} if for every pair of $k$-uple $((\alpha_1, \dots, \alpha_k), (\beta_1, \dots, \beta_k)$ with $\alpha_i, \beta_i \in \Omega$ there exists at least one $g \in G$ such that $\alpha_i g = \beta_i \  \forall i$.
\end{definition}

\begin{definition}[Sharp $k$-transitive group]\index{sharp k-transitive group}
  A permutation group $G$ on $\Omega$ is called \textit{sharp $k$-transitive} if for every pair of $k$-uple $((\alpha_1, \dots, \alpha_n), (\beta_1, \dots, \beta_n)$ with $\alpha_i, \beta_i \in \Omega$ there exists exactly one $g \in G$ such that $\alpha_i g = \beta_i \  \forall i$.
\end{definition}

\begin{property}
  \label{practical-transitivity}
  A group is $k$-transitive if it is $(k-1)$-transitive and if there are $k-1$ points that can be fixed while one other point can be permuted with any non fixed point i.e. if the stabilizer of $k-1$ points is transitive.
\end{property}

\subsection{Primitive groups}

\begin{definition}[Congruence]
  A congruence $\sim$ is an equality relation on $\Omega$ such that $\alpha \sim \beta \Leftrightarrow \alpha g \sim \beta g \ \forall g \in G$.
\end{definition}

There are two trivial congruences on all permutation groups:
\begin{itemize}
  \item Equality
  \item Universal relation i.e. $\alpha \sim \beta \quad \forall \alpha, \beta \in \Omega$.
\end{itemize}

\begin{definition}[Primitive group]
  A group is called \textit{primitive} if it does not have any non-trivial congruence.
\end{definition}

\begin{property}
  \label{2-transitive-primitive}
  Every 2-transitive permutation group is primitive.
\end{property}

\paragraph{}
For the proof, see for instance Theorem~1.7 of~\cite{cameronPermutationGroups}.

\subsection{String groups generated by involutions}

\begin{definition}[Involution]
  An element $g$ of a group is called an \textit{involution} if $g \neq \id$ and $g^2 = \id$.
\end{definition}

\begin{definition}[Indexed generated group]
  Let $G$ be a group and let $S = \{\rho_0, \dots, \rho_{r-1}\}$ be an indexed set of generators.
  We call the pair $(G,S)$ an \textit{indexed generated group}. It is denoted $\Gamma$.
\end{definition}

\begin{definition}[Rank of an indexed generated group]
  The rank of an indexed generated group is the number of generators, i.e. the size of $S$.
\end{definition}

\begin{definition}[Group generated by involutions]
  Let $\Gamma$ be an indexed generated group. If all the generators of this group are involutions, then this group is called a \textit{group generated by involutions}.
\end{definition}

\begin{definition}[String property]
  Let $\Gamma$ be an indexed generated group of rank $r$. If for all $0 \le i \le i + 2 \le j \le r-1$, $\rho_i$ and $\rho_j$ commutes i.e. $\rho_i \rho_j = \rho_j\rho_i$, then this indexed generated group has the \textit{string property}.
\end{definition}

\begin{definition}[String group generated by involution]
  If a group generated by involutions has the string property, we call it a \textit{string group generated by involution} or \textit{sggi}.
\end{definition}

\begin{definition}[Monodromy group]
  A monodromy group is sggi such that its generators are independent.
\end{definition}

\subsection{String C-groups}

\paragraph{}
Let $\Gamma = (G,S)$ be an indexed generated group. We denote $\Gamma_I$ with $I \subseteq S$ the permutation group by $I$.

\begin{definition}[Intersection property]
  Let $\Gamma = (G,S)$ be a indexed generated group. If for all $I, J \subseteq S$, we have that $\Gamma_I \cap \Gamma_J = \Gamma_{I \cap J}$, we say that $\Gamma$ satisfies the intersection property.
\end{definition}

\begin{definition}[String C-group]
  If a sggi satisfies the intersection property, we say that is a $\textit{string C-group}$.
\end{definition}

\begin{property}
  \label{not-monodromy-intersection}
  An sggi with non independent generators (i.e. not a monodromy group), cannot satisfy the intersection property and thus cannot be a string C-group representation.
\end{property}
