\section{Polytopes}

\subsection{Euclidean polytopes}
\begin{definition}[Convex hull]
  \index{convex hull}
  The \textit{convex hull} of a finite set of points $\{x_1 \dots x_n\}$ is the set of points determined by
  \[
    y = \sum_{i=1}^n \lambda_i x_i
  \]
  such that
  \[
    \sum_{i=1}^n \lambda_i = 1
  \]
  \[
    \lambda_i \ge 0 \quad \forall i
  \]
\end{definition}

\begin{definition}[$\mathcal V$-polytope]
  A $\mathcal V$-polytope is the convex hull of a finite number of points.
\end{definition}

\begin{definition}[$\mathcal H$-polytope]
  A $\mathcal H$-polytope is a bounded intersection of a finite number of closed half-planes.
\end{definition}

\begin{theorem}
  A subset $\mathcal P \subseteq \mathbb R^d$ is a $\mathcal V$-polytope iff it's a $\mathcal H$-polytope.
\end{theorem}

\paragraph{}
For the proof see for instance Theorem~1.1 of~\cite{polytopes}

\paragraph{}
There are two ways to represent polytopes and the most adapted representation will be used in every statement.

\paragraph{}
The equation of a half plane is of the form $Ax \le c$. Each half plane can be summarized as a couple $(A,c)$. If the half planes are indexed by $i$, then a polytope is a set points $x$ such that $A_i x \le c_i$ for all $i$.

\begin{definition}[Valid inequality]
  An inequality $ax \le c$ is valid for a polytope $P$ if it is satisfied for all points $x \in \mathcal P$.
\end{definition}

\begin{definition}[Face of polytope]
  A face of a polytopes $\mathcal P$ is the intersection between $\mathcal P$ and the hyperplane determined by $Ax = c$ where $Ax \le c$ is a valid inequality. By convention, $\mathcal P$ itself is also a face of $\mathcal P$ with $A=0$ and $c=0$.
\end{definition}

\begin{definition}[Face lattice]
  For every polytope $\mathcal P$, the face lattice of $\mathcal P$, noted $L(\mathcal P)$ is a poset. The elements of the face lattice are the faces of $\mathcal P$. Given two faces $F$ and $G$ of $\mathcal P$, $F \le G$ iff $F \subseteq G$.
\end{definition}

\begin{property}
  $L(\mathcal P)$ is a graded poset of length $\dim(F) + 1$ with rank function : $\rank(F) = \dim(F) + 1$.
\end{property}

\begin{proposition}
  Let $\mathcal P$ be a convex polytope and $L(\mathcal P)$ its face lattice:

  \begin{enumerate}
    \item \textbf{(P1)} $L(\mathcal P)$ has a maximum element called $\mathcal P$ and a minimum element denoted $\emptyset$.
    \item \textbf{(P2)} Every maximal chain of $L(\mathcal P)$ has a length $n + 2$.
    \item \textbf{(P3)} $L(\mathcal P)$ is strongly connected.
    \item \textbf{(P4)} $L(\mathcal P)$ satisfies the diamond property.
  \end{enumerate}
\end{proposition}
