\chapter{Proof for rank 5}

\paragraph{}
In this chapter we consider polytopes of rank 5. Thus there are 5 generators : $\rho_0, \rho_1, \rho_2, \rho_3, \rho_4$. We want to prove that there are no regular polytopes of rank 5 with automorphism group $A_{11}$. This is equivalent to prove that there exist no string C-group of rank 5 generating $A_{11}$.

\paragraph{}
By Lemma~\ref{min-4-trans} we know that at least one of the $\rho_i$'s is a 4-transposition. We first exclude the case where $\rho_0$ is a 4-transposition in Lemma~\ref{exclude-0}. By duality the case where $\rho_4$ is a 4-transposition is also excluded. We then exclude the case where $\rho_1$ is a 4-transposition in Lemma~\ref{exclude-1}. $\rho_3$ is also excluded by duality. Thus $\rho_2$ must be a 4-transposition. Given this condition, we find some sggis in Lemma~\ref{find-2} but we prove in Lemma~\ref{exclude-2} that none of them are C-groups.

\paragraph{}
Thus there are no regular polytopes of rank 5 with $A_{11}$ as automorphism group.

\section{$\rho_0$ cannot be a 4-transposition}

\begin{lemma}
  \label{exclude-0}
  $\rho_0$ (and thus $\rho_4$) cannot be a 4-transposition.
\end{lemma}

\begin{proof}
  Suppose that $\rho_0$ is a 4-transposition. Then $\rho_0$ permutes 8 points and leave 3 other points fixed. As $\rho_4$ is either a 2-transposition or a 4-transposition, it must permute at least 4 points. Since $\rho_0$ has only 3 fixed points, at least one point is moved by $\rho_0$ and $\rho_4$ but that is in contradiction with Lemma~\ref{0-4-no-share}.
\end{proof}
